### 2014-03-14 Draft/introduction.tex
Fixed bib entries and references

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

@@

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item An NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
	\item An evaluation of proposed approach on commonly used package \CodeIn{java.io} from JDK API and \amazonAPI. 
\end{itemize}

>>>>

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Although, existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

@@

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item An NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
	\item An evaluation of proposed approach on commonly used package \CodeIn{java.io} from JDK API and \amazonAPI. 
\end{itemize}

### 2014-03-14 Draft/related.tex
Fixed bib entries and references

\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
Design by contracts has been an influential concept in the area of software engineering in the past decade.
A significant amount of work has been done in automated inference of code contracts.
There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan:2001:HAA:647540.730008}.
Furthermore, there are existing approaches that infer code-contract-like specifications
(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} from source code and binaries.
In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.

>>>>

\subsection{Code Contracts - Formal Specifications}
% Define temporal constraints distinction
Design by contracts has been an influential concept in the area of software engineering in the past decade.
A significant amount of work has been done in automated inference of code contracts.
There are existing approaches that statically or dynamically extract code contracts~\cite{csallner08dysy,NimmerE02:ISSTA,Tillmann:2006:DLM:2105385.2105433}. However, a combination of developer written and automatically inferred contracts seems to be the most effective approach~\cite{Polikarpova2009ISSTA,Flanagan2001:HAA}.
Furthermore, there are existing approaches that infer code-contract-like specifications
(such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries.
In contrast, the approach presented in this work infers specifications from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.
